### 2024-05-30 thesis/input_files/analysis.tex
scores kernel comparison
gefcomeprice update end

\begin{table}[!ht]
    \centering
    \caption{Pinball loss kernel comparison for load in Switzerland (2021)}
    \label{tab:secures_met_ch}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{llllllllll}
    \toprule
    Quantile & Gaussian RBF & Laplacian & Matern 1.5 & Matern 2.5 & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
    \midrule
    0.1 & 0.018861 & \textbf{0.018798} & 0.019285 & 0.019510 & 0.019128 & 0.024474 & 0.021105 & 0.024299 & 0.018996 \\
    0.2 & 0.030924 & \textbf{0.030430} & 0.031038 & 0.031438 & 0.031223 & 0.040274 & 0.033892 & 0.039774 & 0.031008 \\
    0.3 & 0.039107 & \textbf{0.038510} & 0.039295 & 0.039751 & 0.039637 & 0.051023 & 0.042683 & 0.050242 & 0.039363 \\
    0.4 & 0.044285 & \textbf{0.043718} & 0.044763 & 0.045143 & 0.045130 & 0.057785 & 0.048232 & 0.056815 & 0.044896 \\
    0.5 & 0.046840 & \textbf{0.046261} & 0.047502 & 0.047957 & 0.047739 & 0.060671 & 0.051024 & 0.059697 & 0.047302 \\
    0.6 & 0.046138 & \textbf{0.045582} & 0.047239 & 0.047686 & 0.047416 & 0.059627 & 0.050456 & 0.058824 & 0.046834 \\
    0.7 & 0.041910 & \textbf{0.041615} & 0.043404 & 0.043964 & 0.043735 & 0.054688 & 0.046437 & 0.054037 & 0.042897 \\
    0.8 & 0.034032 & \textbf{0.033852} & 0.035332 & 0.035997 & 0.035518 & 0.044591 & 0.037918 & 0.044112 & 0.034557 \\
    0.9 & \textbf{0.021817} & 0.021923 & 0.022712 & 0.023082 & 0.022721 & 0.028070 & 0.024161 & 0.027920 & 0.022606 \\
    \midrule
    CRPS & 0.035990 & \textbf{0.035632} & 0.036730 & 0.037170 & 0.036916 & 0.046800 & 0.039545 & 0.046191 & 0.036495 \\
    \bottomrule
    \end{tabular}
\end{adjustbox}
    \end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Germany (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & 0.027483 & 0.027827 & 0.028236 & 0.028257 & 0.028057 & 0.028261 & 0.028277 & 0.028276 & 0.028146 & 0.028004 \\
        0.2 & 0.046051 & 0.046679 & 0.047531 & 0.047544 & 0.047118 & 0.047569 & 0.047595 & 0.047596 & 0.047353 & 0.047025 \\
        0.3 & 0.058739 & 0.059835 & 0.060892 & 0.060940 & 0.060366 & 0.060962 & 0.060988 & 0.060984 & 0.060654 & 0.060209 \\
        0.4 & 0.066347 & 0.067768 & 0.068952 & 0.069022 & 0.068344 & 0.069054 & 0.069104 & 0.069101 & 0.068634 & 0.068202 \\
        0.5 & 0.069118 & 0.070761 & 0.072188 & 0.072250 & 0.071450 & 0.072285 & 0.072331 & 0.072330 & 0.071807 & 0.071359 \\
        0.6 & 0.067098 & 0.068276 & 0.069454 & 0.069526 & 0.068821 & 0.069571 & 0.069615 & 0.069613 & 0.069157 & 0.068780 \\
        0.7 & 0.059972 & 0.060783 & 0.061382 & 0.061410 & 0.061150 & 0.061427 & 0.061442 & 0.061442 & 0.061281 & 0.060990 \\
        0.8 & 0.046457 & 0.046944 & 0.047325 & 0.047331 & 0.047147 & 0.047340 & 0.047348 & 0.047349 & 0.047247 & 0.047056 \\
        0.9 & 0.026343 & 0.026554 & 0.026749 & 0.026757 & 0.026646 & 0.026763 & 0.026772 & 0.026772 & 0.026282 & 0.026628 \\
        \midrule
        CRPS & 0.051956 & 0.052825 & 0.053634 & 0.053671 & 0.053233 & 0.053693 & 0.053719 & 0.053718 & 0.053395 & 0.053139 \\
        \bottomrule
        \end{tabular}
\end{adjustbox}
\end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
    0.100000 & 0.023882 & 0.027901 & 0.024316 & 0.024611 & 0.024309 & 0.029367 & 0.029462 & 0.027319 & 0.029459 & 0.027816 \\
    0.200000 & 0.040318 & 0.046043 & 0.040987 & 0.041487 & 0.041028 & 0.048510 & 0.048716 & 0.046164 & 0.048714 & 0.045879 \\
    0.300000 & 0.051643 & 0.058812 & 0.052548 & 0.052972 & 0.052597 & 0.062242 & 0.062561 & 0.059133 & 0.062548 & 0.058454 \\
    0.400000 & 0.057676 & 0.066704 & 0.058841 & 0.059078 & 0.058803 & 0.070210 & 0.070577 & 0.067914 & 0.070567 & 0.066335 \\
    0.500000 & 0.059441 & 0.071401 & 0.060912 & 0.061541 & 0.060846 & 0.073399 & 0.073782 & 0.071616 & 0.073764 & 0.069574 \\
    0.600000 & 0.057820 & 0.067650 & 0.059237 & 0.059930 & 0.059336 & 0.070817 & 0.071157 & 0.070249 & 0.071134 & 0.066970 \\
    0.700000 & 0.052402 & 0.059061 & 0.053949 & 0.054372 & 0.053937 & 0.062453 & 0.062688 & 0.062970 & 0.062675 & 0.059419 \\
    0.800000 & 0.042427 & 0.047954 & 0.043364 & 0.043510 & 0.043366 & 0.049024 & 0.049150 & 0.049737 & 0.049147 & 0.046662 \\
    0.900000 & 0.026227 & 0.028459 & 0.026645 & 0.026817 & 0.026727 & 0.029516 & 0.029601 & 0.030097 & 0.029598 & 0.027986 \\
    \midrule
    CRPS & 0.045760 & 0.052665 & 0.046755 & 0.047146 & 0.046772 & 0.055060 & 0.055299 & 0.053911 & 0.055290 & 0.052122 \\
    \bottomrule
    \end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Gaussian RBF is the second best in terms of pinball loss.

@@

Our results for this track are reported in Table \ref{tab:pinball loss gefcom2014 price data}. In this track, the top entries came from the teams: Tololo, Team Poland, GMD, and C3 Green Team; for a breakdown of each method's attributes, see \cite[Table 8]{hong2016probabilistic}. Finally, the Gaussian RBF probabilistic prediction for the $13^{th}$ July $2013$ zonal price at the $90\%$ confidence interval is visualized in Figure \ref{fig:price_task_6_gaussian_rbf}.

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_6_gaussian_rbf.png}
    \caption[Prediction price track task 6, Gaussian RBF kernel]{Price 90\% confidence interval task 6. Electricity price probabilistic forecast for the $13^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively}
    % \Description{}
    \label{fig:price_task_6_gaussian_rbf}
\end{figure}

\begin{table}[!ht]
    \centering
    \caption{Pinball loss GEFCom2014 price data}
    \label{tab:pinball loss gefcom2014 price data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name\textbackslash Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12               \\
  KQR Laplacian
  &
  \textbf{1.3249}
  &
  2.9497
  &
  0.8868
  &
  7.3780
  &
  5.4314
  &
  8.2166
  &
  4.9091
  &
  1.5245
  &
  1.9601
  &
  2.7324
  &
  2.4733
  &
  17.5371
  \\
  KQR Gaussian RBF
  &
  2.0614
  &
  3.2247
  &
  \textbf{0.7050}
  &
  6.1407
  &
  6.1134
  &
  8.5969
  &
  2.9360
  &
  1.5731
  &
  1.8830
  &
  2.6419
  &
  2.4814
  &
  16.1921
  \\
  \\

>>>>

\begin{table}[!ht]
    \centering
    \caption{Pinball loss kernel comparison for load in Switzerland (2021)}
    \label{tab:secures_met_ch}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lllllllllll}
            \toprule
            Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
            \midrule
            0.1 & \textbf{0.018783} & 0.018988 & 0.019108 & 0.019257 & 0.019547 & 0.019952 & 0.018891 & 0.019654 & 0.021456 & 0.021921 \\
            0.2 & \textbf{0.030441} & 0.030668 & 0.030809 & 0.031028 & 0.031546 & 0.032158 & 0.030683 & 0.031857 & 0.034032 & 0.034629 \\
            0.3 & \textbf{0.038467} & 0.038864 & 0.039050 & 0.039285 & 0.039907 & 0.040657 & 0.038968 & 0.040075 & 0.042944 & 0.043393 \\
            0.4 & \textbf{0.043622} & 0.044186 & 0.044516 & 0.044706 & 0.045286 & 0.046153 & 0.044354 & 0.045506 & 0.048701 & 0.048977 \\
            0.5 & \textbf{0.046160} & 0.046792 & 0.047205 & 0.047450 & 0.048116 & 0.048951 & 0.046956 & 0.047891 & 0.051423 & 0.051896 \\
            0.6 & \textbf{0.045499} & 0.046133 & 0.046824 & 0.047177 & 0.047840 & 0.048667 & 0.046446 & 0.047496 & 0.051292 & 0.051894 \\
            0.7 & \textbf{0.041494} & 0.042044 & 0.042928 & 0.043371 & 0.044104 & 0.044926 & 0.042458 & 0.043565 & 0.047656 & 0.048275 \\
            0.8 & \textbf{0.033837} & 0.034128 & 0.034797 & 0.035325 & 0.036166 & 0.037055 & 0.034290 & 0.035533 & 0.039501 & 0.040007 \\
            0.9 & \textbf{0.021883} & 0.021871 & 0.022431 & 0.022682 & 0.023169 & 0.023730 & 0.022000 & 0.022811 & 0.025561 & 0.026019 \\
            \midrule
            CRPS & \textbf{0.035576} & 0.035964 & 0.036407 & 0.036698 & 0.037298 & 0.038028 & 0.036116 & 0.037154 & 0.040285 & 0.040779 \\
            \bottomrule
    \end{tabular}
\end{adjustbox}
    \end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Germany (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & \textbf{0.025734} & 0.026272 & 0.026642 & 0.026845 & 0.027090 & 0.027306 & 0.026139 & 0.026621 & 0.027954 & 0.028004 \\
        0.2 & \textbf{0.043114} & 0.044138 & 0.044733 & 0.045057 & 0.045469 & 0.045917 & 0.044088 & 0.044716 & 0.046925 & 0.047025 \\
        0.3 & \textbf{0.054861} & 0.056343 & 0.056930 & 0.057335 & 0.057920 & 0.058528 & 0.056229 & 0.057066 & 0.060092 & 0.060209 \\
        0.4 & \textbf{0.061436} & 0.063490 & 0.064291 & 0.064748 & 0.065433 & 0.066136 & 0.063324 & 0.064683 & 0.067979 & 0.068202 \\
        0.5 & \textbf{0.064144} & 0.066330 & 0.067229 & 0.067696 & 0.068275 & 0.068960 & 0.066325 & 0.071421 & 0.070957 & 0.071359 \\
        0.6 & \textbf{0.062306} & 0.064676 & 0.065836 & 0.066299 & 0.066881 & 0.067405 & 0.064660 & 0.069160 & 0.068494 & 0.068780 \\
        0.7 & \textbf{0.055491} & 0.057851 & 0.058848 & 0.059317 & 0.059878 & 0.060275 & 0.061442 & 0.061423 & 0.060988 & 0.060990 \\
        0.8 & \textbf{0.044023} & 0.045011 & 0.045441 & 0.045644 & 0.046008 & 0.046374 & 0.047348 & 0.047182 & 0.047071 & 0.047056 \\
        0.9 & 0.026178 & \textbf{0.026126} & 0.026160 & 0.026187 & 0.026207 & 0.026282 & 0.026772 & 0.026766 & 0.026581 & 0.026628 \\
        \midrule
        CRPS & \textbf{0.048587} & 0.050026 & 0.050679 & 0.051014 & 0.051462 & 0.051909 & 0.050703 & 0.052115 & 0.053005 & 0.053139 \\
        \bottomrule
        \end{tabular}
\end{adjustbox}
\end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & \textbf{0.024365} & 0.024592 & 0.024550 & 0.024611 & 0.024831 & 0.026853 & 0.025744 & 0.026004 & 0.027672 & 0.027816 \\
        0.2 & \textbf{0.040971} & 0.041406 & 0.041413 & 0.041487 & 0.041857 & 0.045007 & 0.043247 & 0.043720 & 0.045899 & 0.045879 \\
        0.3 & \textbf{0.052316} & 0.052969 & 0.052888 & 0.052973 & 0.053449 & 0.057880 & 0.055231 & 0.055446 & 0.058572 & 0.058454 \\
        0.4 & \textbf{0.058286} & 0.059018 & 0.058916 & 0.059078 & 0.059592 & 0.065770 & 0.061844 & 0.062495 & 0.066599 & 0.066335 \\
        0.5 & 0.060344 & 0.061100 & 0.061319 & 0.061541 & 0.062338 & 0.068197 & 0.063864 & 0.071731 & 0.069761 & 0.069574 \\
        0.6 & \textbf{0.058724} & 0.059507 & 0.059674 & 0.059930 & 0.060709 & 0.065828 & 0.062265 & 0.070269 & 0.067179 & 0.066970 \\
        0.7 & \textbf{0.053148} & 0.054189 & 0.054249 & 0.054372 & 0.054916 & 0.058548 & 0.055830 & 0.063015 & 0.059807 & 0.059419 \\
        0.8 & \textbf{0.042740} & 0.043368 & 0.043408 & 0.043510 & 0.043881 & 0.046017 & 0.044384 & 0.049813 & 0.047078 & 0.046662 \\
        0.9 & \textbf{0.026430} & 0.026583 & 0.026781 & 0.026817 & 0.026908 & 0.027050 & 0.026471 & 0.030279 & 0.028031 & 0.027986 \\
        \midrule
        CRPS & \textbf{0.046369} & 0.046970 & 0.047022 & 0.047146 & 0.047609 & 0.051239 & 0.048764 & 0.052530 & 0.052289 & 0.052122 \\
        \bottomrule
    \end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Gaussian RBF is the second best in terms of pinball loss.

@@

Our results for this track are reported in Table \ref{tab:pinball loss gefcom2014 price data}. In this track, the top entries came from the teams: Tololo, Team Poland, GMD, and C3 Green Team; for a breakdown of each method's attributes, see \cite[Table 8]{hong2016probabilistic}. Finally, the Gaussian RBF probabilistic prediction for the $4^{th}$ July $2013$ zonal price at the $90\%$ confidence interval is visualized in Figure \ref{fig:price_task_4_gaussian_rbf}.

% \begin{figure}[!ht]
%     \centering
%     \includegraphics[width=\linewidth]{images/price_task_6_gaussian_rbf.png}
%     \caption[Prediction price track task 6, Gaussian RBF kernel]{Price 90\% confidence interval task 6. Electricity price probabilistic forecast for the $13^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively}
%     % \Description{}
%     \label{fig:price_task_6_gaussian_rbf}
% \end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_4_gaussian_rbf.png}
    \caption[Prediction price track task 4, Gaussian RBF kernel]{Price 90\% confidence interval task 4. Electricity price probabilistic forecast for the $4^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively}
    % \Description{}
    \label{fig:price_task_4_gaussian_rbf}
\end{figure}

\begin{table}[!ht]
    \centering
    \caption{Pinball loss GEFCom2014 price data}
    \label{tab:pinball loss gefcom2014 price data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name\textbackslash Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12               \\
  KQR Absolute Laplacian
  &
  \textbf{1.02492}
  &
  3.35057
  &
  4.21374
  &
  7.33987
  &
  5.00981
  &
  6.96522
  &
  3.57168
  &
  1.77610
  &
  1.28765
  &
  2.73863
  &
  2.39831
  &
  23.30234
  \\
  KQR Gaussian RBF
  &
  1.84673
  &
  2.81882
  &
  1.54608
  &
  8.31636
  &
  4.05988
  &
  6.60456
  &
  3.57818
  &
  2.02177
  &
  1.45779
  &
  2.20701
  &
  1.98184
  &
  21.41033
  \\
  \\
